---
title: "The Analytics Edge | Unit 1 - Assignment 1"
author: "Fernando Flores"
date: ""
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE, 
               warning = TRUE, #Make it FALSE for distribution
               message = TRUE, #Make it FALSE for distribution
               fig.path = "figure-u1-1/",
               fig.width = 12,
               fig.height = 7)
```


# The Analytical Detective


## Problem 1 - Loading the data

```{r p1_LoadData, cache = TRUE}
mvt <- read.csv("./data_unit1_1/mvtWeek1.csv")
str(mvt)
summary(mvt)
```


### Q.1.1: How many rows of data (observations) are in this dataset?

```{r question1_1}
nrow(mvt)
```


### Q.1.2: How many variables are in this dataset?

```{r question1_2}
ncol(mvt)
```


### Q.1.3: Using the "max" function, what is the maximum value of the variable "ID"?

```{r question1_3}
max(mvt$ID)
```


### Q.1.4: What is the minimum value of the variable "Beat"?

```{r question1_4}
min(mvt$Beat)
```


### Q.1.5: How many observations have value TRUE in the Arrest variable (this is the number of crimes for which an arrest was made)?
```{r question1_5}
nrow(subset(mvt, Arrest == TRUE))
```


### Q.1.6: How many observations have a LocationDescription value of ALLEY?

```{r question1_6}
nrow(subset(mvt, LocationDescription == "ALLEY"))
```



## Problem 2.1 - Understanding Dates in R

In many datasets, like this one, you have a date field. Unfortunately, R does not automatically recognize entries that look like dates. We need to use a function in R to extract the date and time. Take a look at the first entry of Date (remember to use square brackets when looking at a certain entry of a variable).


### Q 2.1: In what format are the entries in the variable Date?

```{r question2_1}
mvt$Date[1]
```

A: Date format is `mm/dd/yy hh:mm`.


## Problem 2.2 - Understanding Dates in R

Now, let's convert these characters into a Date object in R. In your R 
console, type

```{r problem2_2_a}
DateConvert = as.Date(strptime(mvt$Date, "%m/%d/%y %H:%M"))
```

This converts the variable "Date" into a Date object in R. Take a look at 
the variable DateConvert using the summary function.

```{r problem2_2_b}
summary(DateConvert)
```


### Q.2.2: What is the month and year of the median date in our dataset? 
```{r question2_2}
median(DateConvert)
```

A: May 2006





```{r questionX_Y}

```
